Quast Reference Testing

### 2018-11-10 notebooks/quast_reference_testing.Rmd
minor changes

## Genome length vs. reference length
```{r}
ggplot(df2, aes(as.numeric(size), as.numeric(Total.length), fill = short_group))+
  geom_jitter(pch = 21, size = 3)+
  labs(y = "Total Length",
       x = "Reference length",
       fill = NULL)+
  theme_classic()
```

## Genome fraction vs reference length
```{r}
ggplot(df2, aes(as.numeric(Genome.fraction....), as.numeric(Total.length), fill = short_group))+
  geom_jitter(pch = 21, size = 3)+
  labs(y = "Total Length",
       x = "Genome Fraction",
       fill = NULL)+
  theme_classic()
```

>>>>

## Genome fraction vs reference length
```{r}
ggplot(df2, aes(as.numeric(Genome.fraction....), as.numeric(Total.length), fill = short_group))+
  geom_point(pch = 21, size = 3)+
  labs(y = "Total Length",
       x = "Genome Fraction",
       fill = NULL)+
  theme_classic()
```
